Interpretable Machine Learning

### 2018-08-20 talk-40min.Rmd
finishes first draft of slides

## What is Machine Learning

Machine learning is a method for teaching computers to make and improve predictions or behaviours based on data.

@@

# Step 3: Profit. {.center}

@@

# LIME

@@

TODO: find image for explaining shapley value

@@

## What is interpretability?

## When do we need interpretability?

@@

## Examples where we need interpretability

TODO: Insert images
- Credit scores
- Autonomous vehicles
- Medical recommendations
- Automated diagnoses

## When don't we need interpretability?

When we can capture everything in the loss function and the data collection.
only causal relationships.
perfect operationalization of features.

Things that work well. 
Well defined problems

## Example: Digit recognition {.center data-background=images/mnist.jpeg data-background-size=cover}

## What tools do we have?

TODO: replace with image

- Intrinsically interpretable models
- Tools for analyzing specific black box models
- Model-agnostic tools: analysing any black box model
- Interpretability through making data explainable

@@

>>>>

# What is Machine Learning?

<div class="notes">
Machine learning is a method for teaching computers to make and improve predictions or behaviours based on data.
</div>

@@

# Step 3: Profit {.center}

@@

# Local Models (LIME)

@@

## {.center data-background=images/team.jpg data-background-size=contain}

@@

# When do we need interpretability?

## {.center data-background=images/credit.jpg data-background-size=cover}

## {.center data-background=images/pill.jpg data-background-size=cover}

## {.center data-background=images/death.jpg data-background-size=cover}

## {.center data-background=images/people.jpg data-background-size=cover}

@@

# When do we NOT need interpretability?

##  {.center data-background=images/mnist.jpeg data-background-size=cover}

<div class="notes">
When we can capture everything in the loss function and the data collection.
only causal relationships.
perfect operationalization of features.

Things that work well. 
Well defined problems
</div>

# What tools do we have?

<div class="notes">
- Intrinsically interpretable models
- Tools for analyzing specific black box models
- Model-agnostic tools: analysing any black box model
- Interpretability through making data explainable
</div>

@@

# Backup slides

# What is interpretability?

# Statistical Modeling: The Two Cultures

<div class="notes">
Paper by Leo Breiman (Random Forest)
data modeling culture (statistics) vs algorithmic modeling culture (ml)
tradeoff between interpretability and predictive performance
example: tree vs. random forest, logistic regression vs. neural network
</div>

# What makes an explanation human-friendly?

<div class="notes">
short: 1-2 causes
counterfactual: compares to other output
truthful
social context
consistent with prior beliefs
probable
focuses on abnormal causes
</div>
